Near Optimal Behavior with Approximate Abstraction

### 2016-02-04 paper/theory_results.tex
theory res

It follows that the $Q$-value of a state $s$ in $M^T$ for action $a$ is defined by:
% zzz too long... needs to be broken up.

\begin{equation}
Q_T(s, a) = 
\begin{cases}
	   Q_G(s, a) &  T=0\\
	   \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a) &\text{o/w}

@@

% Base Case t=0
\textit{Base Case: $T = 0$}\\
When $T = 0$, $Q_T = Q_G$, so the result trivially follows.
% Base Case t=1
\textit{Base Case: $T = 1$}\\
\begin{align*}
&Q_1(s,a) = \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right].
\end{align*}
Since all co-aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
\begin{align*}
&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_G(s_G, a),\\
&Q_1(s,a) \leq \gamma\sum_{t=0}^{1} \epsilon \gamma^t + Q_G(s_G, a).
\end{align*}
Thus,
\begin{equation}
\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{1}\epsilon \gamma^t
\end{equation}
% Inductive Case
\textit{Inductive Case: $T > 1$}

We assume as our inductive hypothesis that:
\begin{equation}
\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.\\
\end{equation}

@@

By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:

\begin{multline*}
Q_T(s_A, a) = \sum_{g \in G(s_A)}w(g)* \\ 
 \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]
\end{multline*}
Applying our inductive hypothesis yields,
\begin{multline*}
\leq \sum_{g \in G(s_A)}w(g) * \\ \left[ R_G(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]
\end{multline*}
%&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
Then:
\begin{equation*}
\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ w(g)\ Q_G(g,a)\right]
\end{equation*}
Since all aggregated states have Q-values within $\epsilon$ of one another:
\begin{align*}
&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a)\\
&\leq \gamma\sum_{t=0}^{T-1} \epsilon \gamma^t + Q_G(s_G, a)
\end{align*}
Thus,
\begin{equation*}
\left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
\end{equation*}

Since $s_G$ and $s_A$ are arbitrary we conclude
\begin{equation}
\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(\epQ(s_G), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
\end{equation}

As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$.

%Claim 2
\begin{clm}
\label{clm:optAbsActionNearOptGround}
The optimal action in the abstract MDP has a Q-value in the ground which is nearly optimal:

@@

Let $a^*_G$ stand for the optimal action for $s_G$: \\
$a^*_G = \argmin Q_G(s_G, a)$

Let $a^*_A$ stand for the optimal action for $s_A$:\\
 $a^*_A = \argmin Q_A(s_A, a)$

That is, we prove that

\begin{equation}
\label{eq:Q*Claim2}
V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
\end{equation}
\end{clm}

By Claim \ref{clm:closeQs}
\begin{align}
&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma}
\label{eq:Q*OptActionResult}
\end{align}

@@

By definition when $t=0$, $V_G^{\pi_{A,t}} = V_G$ so our bound trivially holds in this case.

@@

We assume for our inductive hypothesis that
\begin{equation}
V_G(s_G) \leq V_G^{\pi_{A,t-1}}(s_G)  + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}
By definition 
\begin{multline*}
V_G^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \\ \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}')
\end{multline*}
Applying our inductive hypothesis yields:
\begin{multline*}
V_G^{\pi_{A,t}}(s_G, a) \geq R_G(s_G, \pi_{A,t}(s_G, a))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)
\end{multline*}
Therefore:
\begin{align*}
%&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q_G(s_G, \pi_{A,t} (s_G))
\end{align*}
Applying Claim \ref{clm:optAbsActionNearOptGround} yields:
\begin{align*}
&\geq \gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G)\\
&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(s_G)
\end{align*}

Thus,
\begin{equation*}
V_G(s_G) \leq V^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation*}
Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.

Thus, from our base case and induction we conclude that
\begin{equation}
\forall_{t, s_G \in \mathcal{S}_g} V^{\pi^*}(s_G) \leq  V^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

Thus, we conclude
\begin{equation*}
\forall_{s_G \in \mathcal{S}_g} V_G(s_G) \leq  V^{\pi_{GA}}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
\end{equation*}

\begin{equation*}
\forall_{s_G \in \mathcal{S}_g} \left | V_G(s_G) - V_G^{\pi_{GA}}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
\end{equation*}

@@

Let $B$ stand for the maximum $Q$-value difference between any pair of ground states in the same abstract state under $\epM$:

\begin{align*}
B = &\max_{s_A, s_1, s_2, a}  |Q_G(s_1, a) - Q_G(s_2, a)|\\
&\text{Where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$.}\\
=&\max_{s_A, s_1, s_2, a}      |\mcR_G(s_1, a) - \mcR_G(s_2, a) +\\
& \gamma \sum_{{s_G}' \in \mcS_G}(\mcT_G(s_1,a,{s_G}')-\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')|
\end{align*}
\begin{multline*}
\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \\ \left[(T_G(s_1, a, {s_G}')-T_G(s_2, a, {s_G}')) 		\max_{a'}Q_G({s_G}', a')	\right]
\end{multline*}
By the similarity of transitions of grouped states under $\epM$:
\begin{align*}
 \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}
\end{align*}
Applying 0-1 reward normalization and algebra:
\begin{equation*}
 \leq \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
\end{equation*}

@@

Here we introduce the approximate abstraction family, $\phi_{bolt}$, which aggregates states with similar Boltzmann distributions on optimal $Q$-values as equivalent. This family of abstractions is appealing as the Boltzmman distribution over $Q$-values has been of interest in the reinforcement learning literature due to its natural balancing of exploration and exploitation~\cite{sutton1998reinforcement}.

\bdefn{$\phi_{bolt}$}
We let $\phi_{bolt}$ define a family of abstractions that, for fixed $\epsilon$ satisfies:
\begin{multline}
\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
\forall_{a} \left|\frac{e^{Q_G^*(s_1,a)}}{\sum_b e^{Q_G^*(s_1,b)}} - \frac{e^{Q_G^*(s_2,a)}}{\sum_b e^{Q_G^*(s_2,b)}}\right| \leq \epsilon
\label{eq:phi_bolt}
\end{multline}
\edefn

We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k\in \mathbb{R}$, of $\epsilon$:
\begin{equation}
\left| \sum_b e^{Q_G^*(s_1,b)} - \sum_b e^{Q_G^*(s_2,b)} \right| \leq k*\epsilon
\label{eq:bolt_denom}
\end{equation}

\begin{lma} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some non-negative constant $k \in \mathbb{R}$::
\begin{equation}
\forall_{s \in \mcS_G} : | V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
\end{equation}
\label{lma:bolt_lemma}
\end{lma}

@@

We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution.

\bdefn{$\ep_{mult}$}
We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies.
\begin{multline}
\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
\forall_{a} \left|\frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)} - \frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)}\right| \leq \epsilon
\end{multline}
\edefn

We also assume that the difference in normalizing terms is bounded by some positive factor, $k \in \mathbb{R}$, of $\epsilon$:
\begin{equation}
\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\epsilon
\end{equation}

\begin{lma} When $S_A$ is created using a function of the $\ep_{mult}$ type, for some non-negative constant $k \in \mathbb{R}$:
\begin{equation}
\forall_{s \in S_M} : | V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}
\end{equation}
\end{lma}

The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma} but without the use of the approximation for $e^x$.

\dnote{Bounds for multi and bolt suspisiously similar. Double check math}

>>>>

It follows that the $Q$-value of a state $s$ in $M^T$ for action $a$ is defined by:
% zzz too long... needs to be broken up.
\begin{equation}
Q_T(s, a) = 
\begin{cases}
	   Q_G(s, a) &  T=0\\
	   \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right] & T = 1\\
	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a) &\text{o/w}

@@

% Base Case t=0
\textit{Base Case: $T = 0$}

When $T = 0$, $Q_T = Q_G$, so the result trivially follows.

% Base Case t=1
\textit{Base Case: $T = 1$}
\begin{align*}
&Q_1(s,a) = \underset{g \in G(s)}{\sum} \left[ w(g)Q_G(g,a) \right].
\end{align*}
Since all co-aggregated states have Q-values within $\epsilon$ of one another and $w(g)$ induces a convex combination,
\begin{align*}
&Q_1(s,a) \leq \epsilon \gamma^t + \epsilon + Q_G(s_G, a),
\end{align*}
Thus,
\begin{equation}
\left| Q_{1}(s_A, a) - Q_G(s_G,a) \right| \leq \sum_{t=0}^{1}\epsilon \gamma^t
\end{equation}
% Inductive Case
\textit{Inductive Case: $T > 1$}

We assume as our inductive hypothesis that:
\begin{equation}
\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.
\end{equation}

@@

By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
\begin{multline*}
Q_T(s_A, a) = \sum_{g \in G(s_A)}w(g)\ * \\ 
 \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right]
\end{multline*}
Applying our inductive hypothesis yields,
\begin{multline*}
\leq \sum_{g \in G(s_A)}w(g)\ * \\ \left[ R_G(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t)      \right]
\end{multline*}
%&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}w(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
Then:
\begin{equation*}
\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ w(g)\ Q_G(g,a)\right]
\end{equation*}
Since all aggregated states have Q-values within $\epsilon$ of one another:
\begin{align*}
\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a) \\
\therefore \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| &\leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
\end{align*}
Since $s_G$ and $s_A$ are arbitrary we conclude
\begin{equation}
\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(\epQ(s_G), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t
\end{equation}

As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore we conclude Equation $\ref{eq:Q*Claim1}$. \\

%Claim 2
\begin{clm}
\label{clm:optAbsActionNearOptGround}
%The optimal action in the abstract MDP has a $Q$-value in the ground which is nearly optimal:

@@

Let $a^*_G$ stand for the optimal action in $s_G$:
\[a^*_G = \argmin Q_G(s_G, a)\]

Let $a^*_A$ stand for the optimal action in $s_A$:
 \[a^*_A = \argmin Q_A(s_A, a)\]

The optimal action in the abstract MDP has a $Q$-value in the ground which is nearly optimal:
\begin{equation}
\label{eq:Q*Claim2}
V_G(s_G) \leq Q_G(s_A, a^*_A) + \frac{2\epsilon}{1-\gamma}
\end{equation}
\end{clm}

By Claim \ref{clm:closeQs}:
\begin{align}
&V_G(s_G) = Q_G(s_G, a^*_G) \leq Q_A(s_G, a^*_G) + \frac{\epsilon}{1-\gamma}
\label{eq:Q*OptActionResult}
\end{align}

@@

By definition when $t=0$, $V_G^{\pi_{A,t}} = V_G$, so our bound trivially holds in this case.

@@

We assume for our inductive hypothesis that
\begin{equation}
V_G(s_G) \leq V_G^{\pi_{A,t-1}}(s_G) + \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}
By definition 
\begin{multline*}
V_G^{\pi_{A,t}}(s_G) = R_G(s, \pi_{A,t}(s_G)) + \\ \gamma \sum_{g'}\mathcal{T}_G(s_G, a, {s_G}')V_G^{\pi_{A,t-1}}({s_G}')
\end{multline*}
Applying our inductive hypothesis yields:
\begin{multline*}
V_G^{\pi_{A,t}}(s_G, a) \geq R_G(s_G, \pi_{A,t}(s_G, a))\ + \\ \gamma \sum_{{s_G}'}\mathcal{T}_G(s_G, a, {s_G}')\left(V_G({s_G}') - \sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} \right)
\end{multline*}
Therefore:
\begin{align*}
%&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + R_G(s, \pi_{A,t}(g)) + \gamma \sum_{g'}\mathcal{T}_G(g, a, g')V^{\pi^*}(g')\\
&\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} + Q_G(s_G, \pi_{A,t} (s_G))
\end{align*}
Applying Claim \ref{clm:optAbsActionNearOptGround} yields:
\begin{align*}
\geq -\gamma\sum_{i=0}^{t-1}\gamma^i \frac{2\epsilon}{1-\gamma} - \frac{2\epsilon}{1-\gamma} + V_{G}(s_G) \\
%&\leq \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma} + V_G(s_G)
\therefore V_G(s_G) \leq V_G^{\pi_{A,t}}(s_G)  + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{align*}
Since $s_G$ was arbitrary, we conclude that our bound holds for all states in $\mathcal{S}_G$ for the inductive case.

Thus, from our base case and induction we conclude that
\begin{equation}
\forall_{t, s_G \in \mathcal{S}_g} V_G^{\pi^*}(s_G) \leq  V_G^{\pi_{A,t}}(s_G) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

Thus, we conclude Lemma~\ref{lma:Q*}
%\begin{equation*}
%\forall_{s_G \in \mathcal{S}_g} V_G(s_G) \leq  V_G^{\pi_{GA}}(s_G) + \frac{2\epsilon}{(1-\gamma)^2}
%\end{equation*}
%\begin{equation*}
%\forall_{s_G \in \mathcal{S}_g} \left | V_G(s_G) - V_G^{\pi_{GA}}(s_G) \right | \leq  \frac{2\epsilon}{(1-\gamma)^2}
%\end{equation*}

@@

Let $B$ stand for the maximum $Q$-value difference between any pair of ground states in the same abstract state under $\epM$:
\begin{equation*}
B = \max_{s_A, s_1, s_2, a}  |Q_G(s_1, a) - Q_G(s_2, a)|
\end{equation*}
Where $s_A \in \mcS_G$ and $s_1, s_2 \in G(s_A)$.:
\begin{multline*}
=\max_{s_A, s_1, s_2, a}      |\mcR_G(s_1, a) - \mcR_G(s_2, a) +\\
\gamma \sum_{{s_G}' \in \mcS_G}(\mcT_G(s_1,a,{s_G}')-\mcT_G(s_2, a, {s_G}'))\max_{a'}Q_G({s_G}', a')|
\end{multline*}
\begin{multline*}
\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{{s_G}' \in G(s_A)} \\
\left[(T_G(s_1, a, {s_G}')-T_G(s_2, a, {s_G}')) \max_{a'}Q_G({s_G}', a') \right]
\end{multline*}
By the similarity of transitions of grouped states under $\epM$:
\begin{align*}
 \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}
\end{align*}
Applying 0-1 reward normalization and algebra:
\begin{equation*}
 \leq \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
\end{equation*}

@@

Here we introduce the approximate abstraction family, $\phi_{bolt}$, which aggregates states with similar Boltzmann distributions on optimal $Q$-values as equivalent. This family of abstractions is appealing as the Boltzmman distribution over $Q$-values has been of interest in the reinforcement learning literature due to its natural balancing of exploration and exploitation~\cite{sutton1998reinforcement}.
\bdefn{$\phi_{bolt}$}
We let $\phi_{bolt}$ define a family of abstractions that, for fixed $\epsilon$ satisfies:
\begin{multline}
\ep_{bolt}(s_1) = \ep_{bolt}(s_2) \rightarrow \\
\forall_{a} \left|\frac{e^{Q_G^*(s_1,a)}}{\sum_b e^{Q_G^*(s_1,b)}} - \frac{e^{Q_G^*(s_2,a)}}{\sum_b e^{Q_G^*(s_2,b)}}\right| \leq \epsilon
\label{eq:phi_bolt}
\end{multline}
\edefn

We also assume that the difference in normalizing terms is bounded by some non-negative constant, $k\in \mathbb{R}$, of $\epsilon$:
\begin{equation}
\left| \sum_b e^{Q_G^*(s_1,b)} - \sum_b e^{Q_G^*(s_2,b)} \right| \leq k*\epsilon
\label{eq:bolt_denom}
\end{equation}
\begin{lma} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some non-negative constant $k \in \mathbb{R}$::
\begin{equation}
\forall_{s \in \mcS_G} : \left| V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \right| \leq \frac{2\epsilon\left(\frac{|\mathcal{A}|}{1-\gamma} + k\epsilon + k\right)}{(1-\gamma)^2}
\end{equation}
\label{lma:bolt_lemma}
\end{lma}

@@

We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution.
\bdefn{$\ep_{mult}$}
We let $\phi_{mult}$ define a type of abstraction that, for fixed $\epsilon$ satisfies.
\begin{multline}
\ep_{mult}(s_1) = \ep_{mult}(s_2) \rightarrow \\
\forall_{a} \left|\frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)} - \frac{Q_G^*(s_1,a)}{\sum_b Q_G^*(s_1,b)}\right| \leq \epsilon
\end{multline}
\edefn

We also assume that the difference in normalizing terms is bounded by some positive factor, $k \in \mathbb{R}$, of $\epsilon$:
\begin{equation}
\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\epsilon
\end{equation}
\begin{lma} When $S_A$ is created using a function of the $\ep_{mult}$ type, for some non-negative constant $k \in \mathbb{R}$:
\begin{equation}
\forall_{s \in S_M} : | V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) | \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}
\end{equation}
\end{lma}

{\bf Proof Sketch:} The proof follows an identical strategy to that of Lemma~\ref{lma:bolt_lemma} but without the use of the approximation for $e^x$.

\dnote{Bounds for multi and bolt suspiciously similar. Double check math}
